---
title: "Anomaly_detection"
author: "datagulf"
date: "25/07/2020"
output: html_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Define the Question

This is will help us understand the task at hand, the dataset to be used and the metrics of Success.

### a. Specifying the question.
 Your project has been divided into four parts where you'll explore a recent marketing dataset by performing various unsupervised learning techniques and later providing recommendations based on your insights. 
 
### b. Define the Metrics of Success.
Our metrics of Success is to be able to do a conclusive Dimensionality reduction(Anomaly Detection) through the various methods.

### c. Understand context
The context is using data to do Dimensionality reduction through Anomaly Detection and other ways to get meaningful insights and conclusions from advertising data.

### d. Record the experiment design 
This involves:
a. Cleaning
   i). Removing anomalies in the data
  ii). Finding and dealing with missing data
 iii). Dealing with duplicated rows in the data
 
b. Exploratory Data Analysis
   i). Univariate analysis
  ii). Bivariate analysis
 iii). Multivariate analysis 
 
c. Dimensionality Reduction
   i).  Association Rules
  
### e. Data relevance
To establish if the data is relevant to the question and the objectives of the experiment.

## 2. Read Data
We start by importing the Data

```{r}
library(readr)
fore <- read_csv("Supermarket_Sales_Forecasting - Sales.csv")

```


```{r}
head(fore)
```
```{r}
tail(fore)
```

```{r}
colnames(fore)
```

```{r}
str(fore)
```

```{r}
class(fore)
```
convertion of Dare to a date type 

```{r}
fore$Date <- as.Date(fore$Date,  tryFormats = c("%m-%d-%Y", "%m/%d/%Y"))
#Check the structure
str(fore$Date)
```

```{r}
# Installing anomalize package

install.packages("anomalize")
```
```{r}
# Load tidyverse and anomalize

library(tidyverse)
library(anomalize)
```
```{r}
devtools::install_github("business-science/anomalize")
```
````{r}
fore <- fore %>% rownames_to_column() %>% as_tibble() %>% 
  mutate(date = as.Date(Date)) %>% select(-one_of('Date'))
```

```{r}
super <- fore %>%
  mutate(year = year(date), month = month(date), day = day(date)) %>%
  group_by(year, month, day)%>%
  summarise(sums = mean(Sales))
```



```{r}
fore %>%
  time_decompose(Sales , method = "stl", frequency = "auto", trend = "auto")%>%
  anomalize(remainder, method = "gesd", alpha = 0.05 , max_anoms = 0.2)%>%
            plot_anomaly_decomposition()

```




