---
title: "Association Rules"
author: "datagulf"
date: "26/07/2020"
output: html_document
---

```{r}
library(data.table)
library(readr)
library(tidyverse)
Supermarket <- read.transactions("~/Supermarket_Sales_Dataset II.csv")

```


```{r}
head(supermarket)
```

Check column names
```{r}
colnames(supermarket)
```
Check the dimension
```{r}
dim(supermarket)
```

Check the  class
```{r}
class(supermarket)
```


```{r}
tail(supermarket)
```

```{r}
str(supermarket)
```


```{r}
summary(supermarket)

```
load arules
```{r}
suppressWarnings(
    suppressMessages(if
                     (!require(arules, quietly = TRUE))
            install.packages("arules")))
```

Exploring the frequency of some articles in the data.
View transactions ranging from 10 to 12 and performing 
some operation in percentage terms of the total transactions 

```{r}
library(arules)
```

```{r}
itemFrequency(supermarket[, 10:12],type = "absolute")

```



```{r}
round(itemFrequency(supermarket[, 10:12],type = "relative")*100,2)
```

plot the frequency of items
```{r}

itemFrequencyPlot(supermarket, topN = 10,col="darkgreen")
itemFrequencyPlot(supermarket, support = 0.1,col="darkred")
```

Building a model based on association rules using the apriori function
```{r}
rules <- apriori (supermarket, parameter = list(supp = 0.001, conf = 0.8))
rules
```
Building a apriori model with Min Support as 0.002 and confidence as 0.8


```{r}


rules2 <- apriori (Df, parameter = list(supp = 0.002, conf = 0.8)) 
rules2


```


Building apriori model with Min Support as 0.002 and confidence as 0.6


```{r}
rules3 <- apriori (Df, parameter = list(supp = 0.001, conf = 0.6)) 
rules3


```


```{r}
summary(rules)

```

 Observing rules built in our model i.e. first 6 model rules



```{r}
rules(head)
```

# Order these rules by a criteria such as the level of confidence
# then looking at the first five rules.



```{r}
rules<-sort(rules, by="confidence", decreasing=TRUE)
inspect(rules[1:5])

```
# 1. Determine items that customers who previously bought eggs might buy 



```{r}
eggs <- subset(rules, subset = lhs %pin% "eggs")


```
# Then order by confidence


```{r}
eggs <-sort(eggs, by="confidence", decreasing=TRUE)
head(eggs)


```
# 2. Determine items that customers who previously bought turkey might buy 


```{r}
turkey <- subset(rules, subset = lhs %pin% "turkey")

```
# Then order by confidence
```{r}

turkey <-sort(turkey, by="confidence", decreasing=TRUE)
head(turkey)

```
# 3. Determine which items customers bought before purchasing chocolate

```{r}

chocolate <- subset(rules, subset = rhs %pin% "chocolate")

```

# Then order by confidence
```{r}
chocolate <-sort(chocolate, by="confidence", decreasing=TRUE)
head(chocolate)
```

