---
title: "Dimensionality_reduction"
author: "datagulf"
date: "24/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Define the Question

This is will help us understand the task at hand, the dataset to be used and the metrics of Success.

### a. Specifying the question.
You are a Data analyst at Carrefour Kenya and are currently undertaking a project that will inform the marketing department on the most relevant marketing strategies that will result in the highest no. of sales (total price including tax). Your project has been divided into four parts where you'll explore a recent marketing dataset by performing various unsupervised learning techniques and later providing recommendations based on your insights.
 
### b. Define the Metrics of Success.
Our metrics of Success is to be able to do a conclusive Dimensionality reduction through the various methods.

### c. Understand context
The context is using data to do Dimensionality reduction through PCA and other ways to get meaningful insights and conclusions from advertising data.

### d. Record the experiment design 
This involves:
a. Cleaning
   i). Removing anomalies in the data
  ii). Finding and dealing with missing data
 iii). Dealing with duplicated rows in the data
 
b. Exploratory Data Analysis
   i). Univariate analysis
  ii). Bivariate analysis
 iii). Multivariate analysis 
 
c. Dimensionality Reduction
   i).  Association Rules
  
### e. Data relevance
To establish if the data is relevant to the question and the objectives of the experiment.

## 2. Read Data
We start by importing the Data
```{r }
library(readr)
supermarket <- read_csv("Supermarket_Sales_Dataset II.csv")

```
Check the head
```{r}
head(supermarket)
```

Check the tail
```{r}
tail(supermarket)
```

Check the column names

```{r}
colnames(supermarket)

```
Check the dimensions
```{r}
dim(supermarket)
```

The class of the dataset
```{r}
class(supermarket)

```
Structure
```{r}
str(supermarket)
```



Check the Summary of the supermarket
```{r}
summary(supermarket)
```


```{r}
suppressWarnings(
        suppressMessages(if
                         (!require(Hmisc, quietly=TRUE))
install.packages("Hmisc")))


```
```{r}
describe(supermarket)

```

```{r}
suppressWarnings(
        suppressMessages(if
                         (!require(pastecs, quietly=TRUE))
install.packages("pastecs")))


```

```{r}
library('pastecs')

``` 


```{r}
stat.desc(supermarket)

``` 
Associative Analysis
```{r}
install.packages("arules")
```

```{r}
library(arules)
```

Inspect the class
```{r}
class(supermarket)
```
```{r}
itemFrequency(supermarket, type, weighted = FALSE)

itemFrequency(supermarket, itemsets = FALSE, type = c("absolute", "relative"))
```


```{r}
# Exploring the frequency of some articles 
itemFrequency(supermarket[,10:20],type = "absolute")


```

```{r}
round(itemFrequency(supermarket[, 8:10],type = "relative")*100,2)
```

```{r}

```


```{r}

```


```{r}

```


```{r}

```

```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```

```{r}

```


```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```


```{r}

```


```{r}

```

```{r}

```



